---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# serrrver

<!-- badges: start -->
<!-- badges: end -->

`serrrver` allows you to manage any type of remote server from within R. It proposes one main R6-Class, which initialize a connection to the remote server. Once the connexion is initialized modules can be loaded depending on the use case. For now 2 modules are available: 

1. Docker: allows to manage docker container on the remote server
2. VPN: allows to manage VPN tunnels (for now only compatible with nordvpn) on the remote server

Following modules are planed: 
  1. R: Install R and execute code
  2. Rstudio-server: Run a rstudio-server
  3. Shiny-Server: Run a shiny-server and expose a specific app

## Installation

You can install the released version of serrrver from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("benjaminguinaudeau/serrrver")
```
## Example

```{r}
library(serrrver)
```

```{r}
server <- srv$new(host = "192.168.1.14", user = "pi", port = 22, pwd = Sys.getenv("SERVER_PASS"))
```

## Docker Mod

```{r}
# Init docker module
server$init_docker_mod()

# List containers
server$list_container()
```

## VPN Mod


```{r}
# Init vpn module
server$init_vpn_mod()

# Get ip
server$vpn_ip()
```


## OpenConnect

```{r}
sudo apt install network-manager-openconnect


```

